Is the direction of Granger causal influence the same as the direction of information flow?

### 2015-07-07 paper.tex
Fix Pearl reference page numbers.
Add note about linearity.

In order to compute the Granger causality in the reverse direction (from the receiver to the transmitter), we model $X_i$ as a linear function of its past.
\begin{equation*}
	X_i = \sum_{j=1}^{p}{\alpha_j X_{i-j}} + \epsilon_i \numberthis \label{eq:ar-model-x-x}
\end{equation*}
We then compute coefficients $\alpha_j$ such that the average error in fitting $X_i$ for all $i$ is minimized. Note that $\alpha_j$ can themselves depend on $i$, since this is a non-stationary process (because the error $\Theta-\widehat{\Theta}_i = X_i$ converges to zero). We describe how these coefficients might be estimated in a more general setting, and justify using theoretically determined system parameters as regression coefficients in section~\ref{sec:estimating-ar-coeffs}.

@@

>>>>

In order to compute the Granger causality in the reverse direction (from the receiver to the transmitter), we model $X_i$ as a linear function of its past.
\begin{equation*}
	X_i = \sum_{j=1}^{p}{\alpha_j X_{i-j}} + \epsilon_i \numberthis \label{eq:ar-model-x-x}
\end{equation*}
We then compute coefficients $\alpha_j$ such that the average error in fitting $X_i$ is minimized. Note that $\alpha_j$ can themselves depend on $i$, since this is a non-stationary process (because the error $\Theta-\widehat{\Theta}_i = X_i$ converges to zero). We describe how these coefficients might be estimated in a more general setting, and justify using theoretically determined system parameters as regression coefficients in section~\ref{sec:estimating-ar-coeffs}.

@@

It should be noted that we have restricted ourselves to an analysis of linear strategies: the channel, the extended Schalkwijk and Kailath scheme to a noisy feedback link, and the proposed regression model are all linear.
